Appendix for: "Bad Forecast, Good Decision

### 2021-01-25 manuscript/appendix.Rmd
appendix

scale_colour_discrete <- function(...) ggthemes::scale_colour_solarized()
scale_fill_discrete <- function(...) ggthemes::scale_fill_solarized()
pal <- ggthemes::solarized_pal()(6)
txtcolor <- "#586e75"

@@

policies <- 
  map_dfr(transitions, 
          function(P){
    soln <- mdp(P, reward, discount = discount, 
                epsilon = 0.01, max_iter = 1000, V0 = rep(0,dim(P)[[1]]))
    escapement <- states - actions[soln$policy]
    tibble(states, policy = soln$policy, escapement)
    }, 
  .id = "model")
```

>>>>

scale_colour_discrete <- function(...) ggthemes::scale_colour_solarized()
scale_fill_discrete <- function(...) ggthemes::scale_fill_solarized()
pal <- ggthemes::solarized_pal()(8)
txtcolor <- "#586e75"

@@

policies <- 
  map_dfr(transitions, 
          function(P){
    soln <- mdp(P, reward, discount = discount, 
                epsilon = 0.01, max_iter = 2000, V0 = rep(0,dim(P)[[1]]))
    escapement <- states - actions[soln$policy]
    tibble(states, policy = soln$policy, escapement)
    }, 
  .id = "model")
```

# Adaptive Management

Passive adaptive management using a Bayesian learning scheme still learns the wrong model.

```{r}
adaptive_management <- memoise::memoise(mdp_learning, cache = memoise::cache_filesystem("cache/"))
x0 <- which.min(abs(states - 6))

am1 <- adaptive_management(transitions[1:2], reward, discount, model_prior = c(0.99, 0.01), x0 = x0, 
               Tmax = 50, true_transition = transitions[[3]], 
                epsilon = 0.001, max_iter = 2000)
```

```{r}
am <- am1$df %>% mutate(belief = am1$posterior$V2)
am %>%  ggplot(aes(time, states[state], col = belief)) + geom_line() + geom_point() +  scale_colour_gradient(limits = c(0,1), low = pal[1], high = pal[4])
```

```{r include = FALSE}
as_tibble(am1$posterior) %>% 
  mutate(time = seq_along(V1)) %>%
  select(time = time, "1" = V1, "2" = V2) %>% 
  pivot_longer(c("1", "2"), values_to="belief", names_to = "model") %>%
  filter(time < 20) %>%
  ggplot(aes(time, belief, col=model)) + geom_line(col = pal[4])
```
